The state of knowledge for marine invertebrate biodiversity in the continental US

### 2018-01-18 manuscript.Rmd
add justification of search by coordinates in methods section

>>>>

We opted to limit our queries to records with geographic coordinates instead of relying on the "Country" fields of these databases. Tests showed that these queries would return numerous records outside the geographic range of interest for this study (for instance records collected in Hawaii, Alaska, or the US Virgin Islands), while not taking into account records falling within the US EEZ where the "Country" field contained "Atlantic Ocean" for instance.
